Reduced diversity and increased specialization of Alaska salmon fishermen:

### 2017-03-11 salmon/paper/salmon_paper_v3.Rmd
updated bib and paper

Increasing trends toward specialization in Alaska salmon fisheries may be acceptable for fishers, if individuals are willing to accept the additional risk that may accompany large revenues. Variability in the revenues that individuals or communities experience is by product of many complex drivers, including management, market forces, and environmental variation. While reducing risks to individual fisher revenues is not something that can currently be managed for, understanding patterns of variability that individuals experience is essential for quantifying changing revenue patterns at higher levels of fisheries and coastal communities, and protecting individuals from future economic shocks.

>>>>

Increasing trends toward specialization in Alaska salmon fisheries may be acceptable for fishers, if individuals are willing to accept the additional risk that may accompany large revenues, particularly when prices and abundances are high. Variability in the revenues that individuals or communities experience is by product of many complex drivers, including management, market forces, and environmental variation. While reducing risks to individual fisher revenues is not something that can currently be managed for, understanding patterns of variability that individuals experience is essential for quantifying changing revenue patterns at higher levels of fisheries and coastal communities, and protecting individuals from future economic shocks.
